NHF1 Deamination Sequence and Position Figure Generation

### 2022-05-19 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           "deamination_anchored_excision_site_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

>>>>

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           "deamination_anchored_excision_site_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

### 2022-05-19 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

>>>>

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
filtering = character()

### 2022-05-19 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

>>>>

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

### 2022-05-19 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

>>>>

```{r CPD_read_length_distributions}
plotReadLengthFrequencies(CPDMismatchData$rep1, title = "CPD Read Length Freq Rep 1")
plotReadLengthFrequencies(CPDMismatchData$rep2, title = "CPD Read Length Freq Rep 2")
```

```{r 6-4_read_length_distributions}
plotReadLengthFrequencies(sixFourMismatchData$rep1, title = "6-4 Read Length Freq Rep 1")
plotReadLengthFrequencies(sixFourMismatchData$rep2, title = "6-4 Read Length Freq Rep 2")
```
